Recognizing emotions with technology and starting discussions

### 2018-01-21 paper.tex
Finish results for the most part

\section{Results}
As described in \ref{method}, we have conducted prototype testing sessions with 13 participants. For each of these
participants, we have two pieces of data:
\begin{itemize}
    \item{Predicted emotions during the shown video, created by the prototype}
    \item{Results from the interview we had with each participant during the testing}
\end{itemize}
Furthermore, for every of the three available videos, we have expectations regarding the emotions at certain
times of the video. Using these pieces of data, we are interested in the following information from analyzing
the results:
\begin{enumerate}
    \item{Do the participants agree with the emotions predicted by the prototype?}
    \item{Do the predicted emotions coincide with the expectations we had for certain videos?}
\end{enumerate}
The first questions can be answered by cross-checking the data that the prototype generated, against the
answers from the participants during the interview. The second question can be verified by checking the
expected emotions at certain times in a video, against the average of all the participants who watched that
video. This will make it clear whether the expected emotion is also the dominant emotion at that time.
Finally, we can combine questions 1 and 2. If both results are positive; that is, the predicted emotions by the
prototype match up with our expectations, and are valid according to the participant, then we can conclude
that it's highly likely to be accurate.

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=0.5\textwidth, scale=1]{chart_failarmy_small.png}
    \caption{Average emotions of participants with video "Failarmy"}
\end{figure}

\begin{figure}[h]
    \centering
    \includegraphics[width=0.5\textwidth, scale=1]{chart_neck_small.png}
    \caption{Average emotions of participants with video "Neck"}
\end{figure}

\begin{figure}[h]
    \centering
    \includegraphics[width=0.5\textwidth, scale=1]{chart_roast_small.png}
    \caption{Average emotions of participants with video "Roast"}
\end{figure}

>>>>

\section{Results}
As described in section \ref{method}, we have conducted prototype testing sessions with 13 participants.
For each of these participants, we have two pieces of data:
\begin{itemize}
    \item{Predicted emotions during the shown video, created by the prototype}
    \item{Results from the interview we had with each participant during the testing}
\end{itemize}
Furthermore, for every of the three available videos, we have expectations regarding the emotions at certain
times of the video. Using these pieces of data, we are interested in the following information from analyzing
the results:
\begin{enumerate}
    \item{Do the participants agree with the emotions predicted by the prototype?}
    \item{Do the predicted emotions coincide with the expectations we had for certain videos?}
\end{enumerate}
The first questions can be answered by cross-checking the data that the prototype generated, against the
answers from the participants during the interview. The second question can be verified by checking the
expected emotions at certain times in a video, against the average of all the participants who watched that
video. This will make it clear whether the expected emotion is also the dominant emotion at that time.
Finally, we can combine questions 1 and 2. If both results are positive; that is, the predicted emotions by the
prototype match up with our expectations, and are valid according to the participant, then we can conclude
that it's highly likely to be accurate.

@@

\subsection{Expected emotions}
For each video we had a number of expectations. These differ from general expectation (e.g. a video will be
mostly neutral), or very specific expectations (e.g. at 9 seconds in video "Failarmy" we expect happiness).
Here we enumerate and explain our expectations.

For the first video, \emph{Failarmy}, we expected 5 different moments where the research participant watching
the video would laugh. The reason for this being that this video consists of short humorous clips. These 5
moments are points in the video with climaxes to the clips. Laughter translates to happiness in our prototype,
therefore, there are 5 moments where we expect to see happiness in the charts. As mentioned above,
these are visible in figure \ref{chart_failarmy} as the dashed vertical lines.

For the second video, \emph{Neck}, we expected the majority of the video to be a mix between neutral and disgust.
We expect these emotions in particular because we expect people to not be deeply touched by the beauty
traditions of other cultures. Disgust, in particular, we expect due to not understanding or acknowledging the
culture depicted in the video as valid. Throughout the video, there are two moments in particular where we
expect a spike of disgust. The first is between 23 and 25 seconds. At this moment in the video, a child is first
shown wearing the neck coils. This, combined with the narrator mentioning that adding and maintaining these coils
is "a painful process", cause us to believe that there will be a spike in disgust. Similarly, we expect another
spike between 46 and 49 seconds, due to very comparable reasons; the video shows more coils being added to a
child, and the narrator mentions that "pain is a requirement". These two areas are marked on figure
\ref{chart_neck} as blue colored areas.

For the last video, \emph{Roast}, we expected 6 different points of laughter -- happiness -- throughout
the video. As this was another comedy video, the expected points were moments in which a joke had just been told.
Much like \emph{Failarmy}, these points can be seen on figure \ref{chart_roast} as vertical lines.

\begin{figure}[H]
    \centering
    \includegraphics[width=0.5\textwidth, scale=1]{chart_failarmy_small.png}
    \caption{Average emotions of participants with video "Failarmy"}
    \label{chart_failarmy}
\end{figure}

\begin{figure}[H]
    \centering
    \includegraphics[width=0.5\textwidth, scale=1]{chart_neck_small.png}
    \caption{Average emotions of participants with video "Neck"}
    \label{chart_neck}
\end{figure}

\begin{figure}[H]
    \centering
    \includegraphics[width=0.5\textwidth, scale=1]{chart_roast_small.png}
    \caption{Average emotions of participants with video "Roast"}
    \label{chart_roast}
\end{figure}
